The low-frequency Murchison radio environment:\\interference analysis and mitigation

### 2014-09-05 articles/2014/MWA-Radio-Environment/mwa-radio-environment.tex
Work

\begin{table*}
\caption{List of observations used in the analyses}\label{tbl:obs-list}
\begin{tabular}{|l|l|r|r|r|c|}
\hline
\textbf{Project} &\textbf{Date} & \textbf{Frequencies (MHz)} & \textbf{Duration} & RFI & DVB? \\
\hline
EoR   & 2013-08-23 & 138.8--197.7              & 3h & 0.53\% & ---\\
GLEAM & 2013-08-25 & 72.3--133.8, 138.8--230.8 & 7h & 0.94\% & no \\
EoR   & 2013-08-26 & 138.8--197.7              & 6h & 0.81\% & ---\\
GLEAM & 2013-11-05 & 72.3--133.8, 138.8--230.8 & 7h &  1.3\% & no \\
GLEAM & 2013-11-25 & 72.3--133.8, 138.8--230.8 & 7h & 0.69\% & no \\
EoR   & 2014-02-05 & 138.8--197.7              & 6h & 0.54\% & -- \\
GLEAM & 2014-03-16 & 72.3--133.8, 138.8--230.8 & 7h & 0.79\% & no \\
GLEAM & 2014-03-17 & 72.3--133.8, 138.8--230.8 & 7h & 1.64\% & yes \\
EoR   & 2014-04-10 & 138.8--197.7              & 6h & 0.68\% & ---\\
GLEAM & 2014-06-18 & 72.3--133.8, 138.8--230.8 & 7h & 0.98\% & no \\
RFI test&2014-08-27& 131.2--161.9     & 2$\times$8 m& 1.85\% & --- \\
\hline
\multicolumn{3}{|r|}{\textbf{Total}} & \textbf{63h} & \textbf{0.97\%} & \textbf{1/6}\\
\hline
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\caption{List of observations used in the analyses. The RFI column contains the fraction of visibilities that the initial \textsc{aoflagger} run has detected (which includes false positives). The DVB column displays the fraction of visibilities that were unusable because of the presence of DVB signals. Because the DVB frequencies are only observed in GLEAM observations, this fraction is only given for those. }\label{tbl:obs-list}
\begin{tabular}{|l|l|r|r|r|c|}
\hline
\textbf{Project} &\textbf{Date} & \textbf{Frequencies (MHz)} & \textbf{Duration} & RFI & DVB \\
\hline
EoR   & 2013-08-23 & 138.8--197.7              & 3h & 0.53\% & ---\\
GLEAM & 2013-08-25 & 72.3--133.8, 138.8--230.8 & 7h & 0.94\% & 0\% \\
EoR   & 2013-08-26 & 138.8--197.7              & 6h & 0.81\% & ---\\
GLEAM & 2013-11-05 & 72.3--133.8, 138.8--230.8 & 7h & 1.30\% & 0\% \\
GLEAM & 2013-11-25 & 72.3--133.8, 138.8--230.8 & 7h & 0.69\% & 0\% \\
EoR   & 2014-02-05 & 138.8--197.7              & 6h & 0.54\% & -- \\
GLEAM & 2014-03-16 & 72.3--133.8, 138.8--230.8 & 7h & 0.79\% & 0\% \\
GLEAM & 2014-03-17 & 72.3--133.8, 138.8--230.8 & 7h & 1.64\% & 3\% \\
EoR   & 2014-04-10 & 138.8--197.7              & 6h & 0.68\% & ---\\
GLEAM & 2014-06-18 & 72.3--133.8, 138.8--230.8 & 7h & 0.98\% & 0\% \\
RFI test&2014-08-27& 131.2--161.9     & 2$\times$8 m& 1.85\% & --- \\
\hline
\multicolumn{3}{|r|}{\textbf{Total}} & \textbf{63h} & \textbf{0.97\%} & \textbf{0.5\%}\\
\hline
\end{tabular}
\end{table*}
